Volunteers in the Clouds: A Web Based Architecture to Harness Volunteer Resources for Low Cost Distributed Evolutionary Computation

### 2015-12-10 special-issue-ci/volunteer-clouds-ieee-ci-si.tex
Revising extensively references
Fixing many and adding additional ones. Refs #63.

\begin{abstract}
Volunteer computing is extensively used 
% (Paloma) Adverbs are always written before verbs, check this throughout the text
in science and industry, but it
still has a long way to go in order to become
% (Paloma) I would propose "a long way to go in order to become"
 a mainstream
technology in the same way the cloud technologies in general have. The
lack of % (Paloma) Add "both" here to better complete the sentence
general purpose and open source tools with built-in analytics 
% (Paloma) "built-in" is an adjective and, as such, has to be written before names
could be one of the reasons of why this is so, as well as the lack of
proofs of concept. That is why in this paper we present {\sf NodIO}, a
framework used to create client-server architectures for distributed
evolutionary algorithms, entirely written  % (Paloma) Adverb. I would also add an "and" after the comma
in JavaScript, which needs
minimal server support to work and is able to support persistent,
asynchronous, distributed evolutionary algorithms running in the
browser, as well as any other client consuming its REST application
programming interface.  The architecture, along with some initial
results on the expected performance and scaling behavior when the
number of users is increased is presented. We also use
the algorithm data to find out what kind of patterns the user behavior
follows by examining the resources they devote to our experiment, and
try to fit them to some statistical distribution to create the bases
of a model of user behavior in volunteer computing experiments of this
kind that can be used by researchers to predict its performance. 
In general, our experiments prove, first, that {\sf NodIO} is a flexible and
low-overhead platform to perform distributed computation experiments
that include volunteers, and then that user behavior follows some patterns,
and, thus, are amenable to a model.
\end{abstract}

@@

\IEEEPARstart{N}{owadays} there is a big and increasing number of
distributed evolutionary computation software frameworks available on
the market, usually as open source systems \cite{Parejo12Survey}. Most of these systems have 
two features: they are {\em desktop} applications, that is, they must
be compiled or run directly on the operating system layer and, second,
they assume that the nodes that are going to run the system are under
the control of developers or they at least have access to them.

>>>>

\begin{abstract}
Volunteer computing is extensively used 
in science and industry, but it
still has a long way to go in order to become
 a mainstream
technology in the same way the cloud technologies in general have. The
lack of 
general purpose and open source tools with built-in analytics 
could be one of the reasons of why this is so, as well as the lack of
proofs of concept. That is why in this paper we present {\sf NodIO}, a
framework used to create client-server architectures for distributed
evolutionary algorithms, entirely written  
in JavaScript, which needs
minimal server support to work and is able to support persistent,
asynchronous, distributed evolutionary algorithms running in the
browser, as well as any other client consuming its REST application
programming interface.  The architecture, along with some initial
results on the expected performance and scaling behavior when the
number of users is increased is presented. We also use
the algorithm data to find out what kind of patterns the user behavior
follows by examining the resources they devote to our experiment, and
try to fit them to some statistical distribution to create the bases
of a model of user behavior in volunteer computing experiments of this
kind that can be used by researchers to predict its performance. 
In general, our experiments prove, first, that {\sf NodIO} is a flexible and
low-overhead platform to perform distributed computation experiments
that include volunteers, and then that user behavior follows some patterns,
and, thus, are amenable to a model.
\end{abstract}

@@

\IEEEPARstart{N}{owadays} there is a big and increasing number of
distributed evolutionary computation software frameworks available on
the market, usually as open source systems \cite{Parejo12Survey}. Most of these systems have 
two features: they are {\em desktop} applications, that is, they must
be compiled or run directly on the operating system layer and, second,
they assume that the nodes that are going to run the system are under
the control of developers or they at least have access to them. In
fact, these features are commonly found in most soft computing
frameworks \cite{7094263}.
